LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-12-10 main.tex
Change graphics \input commands to \import
Conflicts:
	main.tex

\begin{figure}
\centering
\setlength\figurewidth{.4\textwidth}
\input{graphics/double_gyre/elliptic_lcs_convergence_500.tikz}
\input{graphics/double_gyre/elliptic_lcs_convergence_750.tikz}
\input{graphics/double_gyre/elliptic_lcs_convergence_1000.tikz}
\caption{Convergence of closed $\lambda$-lines for increasing main-grid resolution in the double-gyre. The outermost closed $\lambda$-line (bold green line) is the vortex boundary. Top: $500 \times 250$, middle: $750 \times 375$, bottom: $1000 \times 500$.}
\label{f:double gyre lambda LCS convergence}
\end{figure}

@@

\begin{figure}
\centering
% FIXME Reviewer #2, comment #6: Improve appearance of $lambda$ extrema (white dots)
\setlength\figurewidth{.35\textwidth}
\input{graphics/double_gyre/elliptic_repelling_lcs_details.tikz}
\input{graphics/double_gyre/elliptic_attracting_lcs_details.tikz}
\caption{
LCSs in the double gyre.
Resolution is $500 \times 250$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00$ and $1.04$ for the left and the right gyre.
$\lambda \in [0.93,1.07]$, $\Delta\lambda = 0.01$.
}
\label{f:double gyre lambda hyperbolic LCS}
\end{figure}

@@

We choose the integration time as $T=30$ days (\cref{l:ocean data elliptic hyperbolic lcs}, \cref{ll:ocean data timespan}), which is larger than the eddy turnover time in this region.
The resolution of the main computational grid for initial conditions is set to $400 \times 400$ (\cref{ll:ocean data resolution}).
This corresponds to a resolution of roughly 0.015° and gives good results.
With this choice, the resolution of the tracer grid is 15 times higher than the resolution of the velocity field.
The flow is integrated and the Cauchy-Green strain tensor is computed by the function \lstinline!eig_cgStrain! (\cref{ll:eig_cgStrain}).
The auxiliary grid distance is set to 1\% of the main grid distance (\cref{ll:cgAuxGridRelDelta}), and eigenvalues are computed from the auxiliary grid (\cref{ll:cgEigenvalueFromMainGrid}).
Elliptic LCSs are computed in \cref{ll:ocean data poincare_closed_orbit_multi}, after the Poincare sections have been set (\cref{ll:ocean data poincareSection(1)}).
$\lambda$-values are varied over a range of $[0.90,1.10]$ with a step of $0.02$ (\cref{ll:ocean data lambdaRange}).
Hyperbolic LCSs are computed in \cref{ll:ocean data shrinkLineLcs,ll:ocean data stretchLineLcs}.

>>>>

\begin{figure}
\centering
\setlength\figurewidth{.4\textwidth}
\import{graphics/double_gyre/}{elliptic_lcs_convergence_500.tikz}
\import{graphics/double_gyre/}{elliptic_lcs_convergence_750.tikz}
\import{graphics/double_gyre/}{elliptic_lcs_convergence_1000.tikz}
\caption{Convergence of closed $\lambda$-lines for increasing main-grid resolution in the double-gyre. The outermost closed $\lambda$-line (bold green line) is the vortex boundary. Top: $500 \times 250$, middle: $750 \times 375$, bottom: $1000 \times 500$.}
\label{f:double gyre lambda LCS convergence}
\end{figure}

@@

\begin{figure}
\centering
% FIXME Reviewer #2, comment #6: Improve appearance of $lambda$ extrema (white dots)
\setlength\figurewidth{.35\textwidth}
\import{graphics/double_gyre/}{elliptic_repelling_lcs_details.tikz}
\import{graphics/double_gyre/}{elliptic_attracting_lcs_details.tikz}
\caption{
LCSs in the double gyre.
Resolution is $500 \times 250$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00$ and $1.04$ for the left and the right gyre.
$\lambda \in [0.93,1.07]$, $\Delta\lambda = 0.01$.
}
\label{f:double gyre lambda hyperbolic LCS}
\end{figure}

@@

We choose the integration time as $T=30$ days (\cref{l:ocean data elliptic hyperbolic lcs}, \cref{ll:ocean data timespan}), which is larger than the eddy turnover time in this region.
The resolution of the main computational grid for initial conditions is set to $400 \times 400$ (\cref{ll:ocean data resolution}).
This corresponds to a resolution of roughly 0.015°.
With this choice, the resolution of the tracer grid is 15 times higher than the resolution of the velocity field.
The flow is integrated and the Cauchy-Green strain tensor is computed by the function \lstinline!eig_cgStrain! (\cref{ll:eig_cgStrain}).
The auxiliary grid distance is set to 1\% of the main grid distance (\cref{ll:cgAuxGridRelDelta}), and eigenvalues are computed from the auxiliary grid (\cref{ll:cgEigenvalueFromMainGrid}).
Elliptic LCSs are computed in \cref{ll:ocean data poincare_closed_orbit_multi}, after the Poincare sections have been set (\cref{ll:ocean data poincareSection(1)}).
$\lambda$-values are varied over a range of $[0.90,1.10]$ with a step of $0.02$ (\cref{ll:ocean data lambdaRange}).
Hyperbolic LCSs are computed in \cref{ll:ocean data shrinkLineLcs,ll:ocean data stretchLineLcs}.
